Inference for trans-dimensional Bayesian models with Diffusive Nested Sampling

### 2014-06-27 Documents/Paper/ms.tex
Heavy tailed proposal details

\section{Metropolis proposals for the general problem}
We will now define a set of proposal distributions that could be used to
sample the prior distribution
$p(N, \hyperparams, \{\xx_i\}) = p(N) p(\hyperparams) \prod_{i=1}^N p(\xx_i | \hyperparams)$.
These proposals will need to satisfy detailed balance in order to be valid
when used inside DNS. The proposals will also be very heavy tailed. When
DNS is exploring a distribution close to the prior, large proposals will
generally be needed. When DNS is exploring a distribution constrained to
very high values of the likelihood function, much smaller proposals will be
appropriate. Rather than attempting expensive tuning (since the number of
distributions involved may number in the hundreds or even thousands), we will
apply the heavy tailed proposal distributions and simply accept that there will
be some waste.

Most of the proposals involve changing one (or a subset) of the parameters
and/or hyperparameters while keeping the others fixed.

>>>>

\section{Metropolis proposals for the general problem}
We will now define a set of proposal distributions that can be used to
sample the prior distribution
$p(N, \hyperparams, \{\xx_i\}) = p(N) p(\hyperparams) \prod_{i=1}^N p(\xx_i | \hyperparams)$.
These proposals will need to satisfy detailed balance in order to be valid
when used inside DNS. When the proposal satisfies detailed balance with respect
to the prior, the DNS algorithm can incorporate hard likelihood constraints by
rejecting any proposal whose likelihood does not satisfy the constraint.
The overall proposal is a mixture of all of the proposals listed here.

When using DNS,
the proposals typically should be very heavy tailed. When
DNS is exploring a distribution close to the prior, large proposals will
generally be needed to explore the prior efficiently.
When DNS is exploring a distribution constrained to
very high values of the likelihood function, much smaller proposals will be
appropriate. Rather than attempting expensive tuning (since the number of
distributions involved may number in the hundreds or even thousands), we will
apply the heavy tailed proposal distributions and simply accept that there will
be some waste. If a parameter $u$ has a uniform prior between 0 and 1, then
a heavy-tailed proposal is defined by:
\begin{eqnarray}
u' &=& \textnormal{mod}\left(u + 10^{1.5 - 6a}b, 1\right)
\end{eqnarray}
where $a \sim \textnormal{Uniform}(0, 1)$ and $b\sim \mathcal{N}(0,1)$. When
$a$ is close to zero, the size of the proposal is of order 10, which (because
of the mod function) effectively randomises $u'$ from the prior. If $a$ is
close to 1, the scale of the proposal is roughly $10^{-4}$ times the prior
width.

Most of the proposals involve changing one (or a subset) of the parameters
and/or hyperparameters while keeping the others fixed, and are heavy-t
